The Ranked Nearest Neighbour Interchange space

### 2019-05-23 paper.tex
minor

\begin{algorithm}[H]
\caption{FIND\_PATH($T_1,T_2$)}
\label{alg:find_path}
\begin{algorithmic}[1]
	\STATE $T := T_1$
	\STATE $p := (T_1)$
	\FOR {$r = 1, \dots, n-2$}
		\STATE Let $S$ be the cluster associated with the node $v$ in $T_2$ with $rank(v) = r$
		\WHILE {$rank(MRCA_T(S))>r$}
			\STATE Update $T$: Decrease $rank(MRCA_T(S))$ by an $\rnni$ move \label{alg:line:move_set_down}
			\STATE $p = p+T$
		\ENDWHILE between these trees
	\ENDFOR
	\RETURN p
\end{algorithmic}
\end{algorithm}

@@

\begin{lemma} between these trees
	There are two caterpillar trees in $\rnniu$ with distance $\frac{1}{2}n^2-\frac{3}{2}n+1$.
	\label{conj:caterpillar_diameter}
\end{lemma}

@@

    In general, deleting taxon $n+1$ and its parent in every tree on any path $p$ from $T$ to $T'$ results in a path $p'$ from $T|_n$ to $T'|n$.
    Such a path $p'$ from $T|_n$ to $T'|n$ does not contain the $n-1$ $\rnni$ moves for moving the parent of $n+1$ down from the root to the cherry, so it is at least $n-1$ $\rnni$ moves shorter than $p$.
    If we assume that there is a path from $T$ to $T'$ of length less than $\Delta(\rnniu_{n+1}) = \frac{n(n-1)}{2}$, we could delete between these trees taxon $n+1$ and the $n-1$ moves of it's parent and receive a path from $T|_n$ to $T'|_n$ of length less than $\frac{n(n-1)}{2} - (n-1)$ = $\frac{(n-1)(n-2)}{2}$.
    So it would be $d(T|_n, T'|_n) < \Delta(\rnniu_n)$.
    Since this is a contradiction to $d(T|_n, T'|_n) = \Delta(\rnniu_n)$, it must be $d(T,T') = \Delta(\rnniu_{n+1}) = \frac{n(n-1)}{2} $.

>>>>

\begin{algorithm}[H]
\caption{FIND\_PATH($T_1,T_2$)}
\label{alg:find_path}
\begin{algorithmic}[1]
	\STATE $T := T_1$
	\STATE $p := (T_1)$
	\FOR {$r = 1, \dots, n-2$}
		\STATE Let $S$ be the cluster associated with the node $v$ in $T_2$ with $rank(v) = r$
		\WHILE {$rank(MRCA_T(S))>r$}
			\STATE Update $T$: Decrease $rank(MRCA_T(S))$ by an $\rnni$ move \label{alg:line:move_set_down}
			\STATE $p = p+T$
		\ENDWHILE
	\ENDFOR
	\RETURN p
\end{algorithmic}
\end{algorithm}

@@

\begin{lemma}
	There are two caterpillar trees in $\rnniu$ with distance $\frac{1}{2}n^2-\frac{3}{2}n+1$.
	\label{conj:caterpillar_diameter}
\end{lemma}

@@

    In general, deleting taxon $n+1$ and its parent in every tree on any path $p$ from $T$ to $T'$ results in a path $p'$ from $T|_n$ to $T'|n$.
    Such a path $p'$ from $T|_n$ to $T'|n$ does not contain the $n-1$ $\rnni$ moves for moving the parent of $n+1$ down from the root to the cherry, so it is at least $n-1$ $\rnni$ moves shorter than $p$.
    If we assume that there is a path from $T$ to $T'$ of length less than $\Delta(\rnniu_{n+1}) = \frac{n(n-1)}{2}$, we could delete taxon $n+1$ and the $n-1$ moves of it's parent and receive a path from $T|_n$ to $T'|_n$ of length less than $\frac{n(n-1)}{2} - (n-1)$ = $\frac{(n-1)(n-2)}{2}$.
    So it would be $d(T|_n, T'|_n) < \Delta(\rnniu_n)$.
    Since this is a contradiction to $d(T|_n, T'|_n) = \Delta(\rnniu_n)$, it must be $d(T,T') = \Delta(\rnniu_{n+1}) = \frac{n(n-1)}{2} $.
